Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-07 paper.tex
minor

Generating a unified co-verification model is a well-known 
technique in HW/SW co-verification.  Notably, Kurshan et al.~modeled HW and 
SW using finite state machines~\cite{fmsd02}, Monniaux in~\cite{emsoft07} modeled
HW and SW as C programs which are formally pushdown systems (PDS), 
Li et al.~in~\cite{fase10} used Buchi Automata to abstractly
model a hardware and PDS to abstractly model a software to generate a unified SW-HW model, 
called Buchi Pushdown System ({\em BPDS}).  In this paper, we construct an unified 
sequential co-verification model in C which enable us to automatically 
generate {\em scenario/transaction} pairs using path-based symbolic execution.

@@

%===============================================================================
\section{Concluding Remarks}
%===============================================================================
%
In this paper, we presented two approaches for verification of 
HW/SW co-designs using formal techniques.  These approaches are 
embodied in our tool \hwcbmcv and \verifox.  We presented a 
notion of scenario and transaction for effective verification 
of co-designs.  To this end, we presented a path-based algorithm
to automatically mine scenario/transaction pairs.  We showed that 
the construction of a co-verification model must leverage specification of 
co-design properties over hardware and firmware events in order to 
successfully apply formal methods in co-verification.  To enable this, we 
presented two types of co-design properties, \emph{transaction level} and 
\emph{component level}.  Our tools support co-designs written in Verilog RTL 
and C.

>>>>

Generating a unified co-verification model is a well-known 
technique in HW/SW co-verification.  Notably, Kurshan et al.~modeled HW and 
SW using finite state machines~\cite{fmsd02}, Monniaux in~\cite{emsoft07} modeled
HW and SW as C programs which are formally pushdown systems (PDS), 
Li et al.~in~\cite{fase10} used Buchi Automata to abstractly
model a hardware and PDS to abstractly model a software to generate a unified SW-HW model, 
called Buchi Pushdown System ({\em BPDS}).  In this paper, we construct a unified 
sequential co-verification model in C which enable us to automatically 
generate {\em scenario/transaction} pairs using path-based symbolic execution.

@@

%===============================================================================
\section{Concluding Remarks}
%===============================================================================
%
In this paper, we presented two approaches for verification of 
HW/SW co-designs using formal techniques.  These approaches are 
embodied in our tools \hwcbmcv and \verifox.  We presented a 
notion of scenario and transaction for effective verification 
of co-designs.  To this end, we presented a path-based algorithm
to automatically mine scenario/transaction pairs.  We showed that 
the construction of a co-verification model must leverage specification of 
co-design properties over hardware and firmware events in order to 
successfully apply formal methods in co-verification.  To enable this, we 
presented two types of co-design properties, \emph{transaction level} and 
\emph{component level}.  Our tools support co-designs written in Verilog RTL 
and C.
